Model LF

### 2022-10-06 max_dp endogen stød.Rmd
Commit

wage_gap_00 = S_model$simulation$wage_gap

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

plot((wage_gap_05), col= "black", xlab= "Year", ylab= "Wage gap as % of target wage", main= "Wage gap");
grid()
```
```{r}
par(mfrow=c(1,2))

plot(((wage_ds_05 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in net balance", main= "Net balance");
grid()

plot(((u_ds_05 - u_ds_00) / u_ds_00), col= "black", xlab= "Year", ylab= "% Change in employment", main= "");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((yk_ds_05 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp");
legend("top", legend=c("GDP"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()

plot(((emp_05 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment");
legend("top", legend=c("Employment"),
       lty=c(1),lwd=c(2),bty="n", col = c("black"));
grid()
```

@@

plot(((kuld_06 - kuld) / kuld), col= "black", xlab= "Year", ylab= "% Change in the insurance rate", main= "Insurance rate");
grid()

plot(((nben_h_06 - nben_h_05) / nben_h_05), col= "black", xlab= "Year", ylab= "% changes in net benefits HH", main= "Net benefits HH", sub= "Compared with scenario 1");
grid()
```

@@

plot(((yk_ds_06 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines()
grid()

@@

@@

## Scenario 1.3 part

@@

 shock_part_model = TIMESERIES(shock_part_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot((yk_ds_01 / yk_ds_00), col= "red", ylim= c(0.995,1.005));
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_02 / yk_ds_00), col= "green");
lines((yk_ds_04 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.998,1.001));
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
lines((yk_ds_07 / yk_ds_00), col= "orange");
legend("top", legend=c(""),
       lty=c(1),lwd=c(2),bty="n", col = c("red"));
grid()
```

>>>>

wage_gap_00 = S_model$simulation$wage_gap
wage_gap_00 = S_model$simulation$shock_kuld

@@

  shock_reg_model = TIMESERIES(shock_reg_model_shock+1 ,START=c(2016,1),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2016,1),  FREQ='Q')

@@

plot(((wage_ds_05 - wage_ds_00) / wage_ds_00), col= "black", xlab= "Year", ylab= "% Change in wages", main= "Wages");
grid()

plot(((pc_ds_05 - pc_ds_00) / pc_ds_00), col= "black", xlab= "Year", ylab= "% Change in consumer prices", main= "Consumer prices");
grid()
```

```{r}
plot(((net_balance_05 - net_balance_00) / net_balance_00), col= "black", xlab= "Year", ylab= "% Change in the net balance", main= "Net balance");
grid()
```

@@

plot(((yk_ds_05 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");

grid()

plot(((emp_05 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in employment", main= "Employment");
grid()
```

@@

plot(((nl_g_06 - nl_g_00)), col= "black", xlab= "Year", ylab= "changes in government net lending", main= "government net lending", ylim= c(-500,1500));
lines(((nl_g_05 - nl_g_00)), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()

plot(((nben_h_06 - nben_h_00) / nben_h_00), col= "black", xlab= "Year", ylab= "% changes in net benefits HH", main= "Net benefits HH");
lines(((nben_h_05 - nben_h_00) / nben_h_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
```

@@

plot(((yk_ds_06 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp");
lines(((yk_ds_05 - yk_ds_00) / yk_ds_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()

@@

plot(((emp_06 - emp_00) / emp_00), col= "black", xlab= "Year", ylab= "% Change in Employment", main= "Employment", ylim= c(-0.0016,0.0002));
lines(((emp_05 - emp_00) / emp_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()

plot(((ur_ds_06 - ur_ds_00) / ur_ds_00), col= "black", xlab= "Year", ylab= "% change in unemployment rate", main= "Unemployment rate ", ylim= c(-0.005,0.03));
lines(((ur_ds_05 - ur_ds_00) / ur_ds_00), col= "red");
legend("left", legend=c("Scenario 3","Scenairo 2"),
       lty=c(1),lwd=c(2),bty="n", col = c("black","red"));
grid()
```

@@

## Scenario 1.3 kuld

@@

 shock_kuld_model = TIMESERIES(shock_kuld_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
  shock_max_dp_model = TIMESERIES(shock_max_dp_model_shock+1 ,START=c(2006,3),  FREQ='Q'),
 shock_wage_ds_model = TIMESERIES(shock_wage_ds_model_shock+1 ,START=c(2006,3),  FREQ='Q')

@@

```{r}
plot((yk_ds_01 / yk_ds_00), col= "red", ylim= c(0.995,1.005), main= "Max_dp follow wages & no supressing");
lines((yk_ds_01w / yk_ds_00), col= "blue");
lines((yk_ds_02 / yk_ds_00), col= "green");
legend("top", legend=c("Demand channel", "Demand & Wage channel", "All channels"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "blue", "green"));
grid()
```

```{r}
plot((yk_ds_01b / yk_ds_00), col= "red", ylim= c(0.998,1.001), main= "No supressing");
lines((yk_ds_05 / yk_ds_00), col= "blue");
lines((yk_ds_06 / yk_ds_00), col= "green");
legend("top", legend=c("Demand channel", "Demand & Wage channel", "All channels"),
       lty=c(1),lwd=c(2),bty="n", col = c("red", "blue", "green"));
grid()
```
